\documentclass[13pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[T1]{fontenc}
\linespread{1.2}
\begin{document}
Student: Minh Pham \\
EID: mlp2279

\begin{center}
	\textbf{Homework 1}
\end{center}

\begin{enumerate}
	\item (10 points)
	Given:
	\begin{verbatim}
	glutInitWindowSize(800, 600);
	gluOrtho2D(-100.0, 100.0, -100.0, 100.0);	
	\end{verbatim}
	
	Convert the following object coordinates to window coordinates.
	
	Solution:
	\begin{tabbing}
	\hspace{20pt} \= Object Coordinates \= Window Coordinates \\
	(a)           \> (0, 0)             \> (400, 300) \\
	(b)           \> (-50, 50)          \> (200, 150) \\
	(c)	          \> (-75, -100)        \> (100, 600) \\
	(d)	          \> (90, 10)           \> (760, 270) \\
	(e)	          \> (0, -40)           \> (400, 420) \\
	\end{tabbing}
	

	\item (5 points)
	Let:
	\begin{enumerate}
	\item[•] $\alpha$, $\beta$, $\gamma$ be scalars
	\item[•] $A$, $B$, $C$ be points
	\item[•] $u$, $v$, $w$ be vectors
	\end{enumerate}
	
	Are the following operations defined? \\
	Answer T/F/? if operation is defined/undefined/don't know.
	\begin{tabbing}
	\hspace{20pt} \= Operation \hspace{20pt} \= Defined?  \\
	(a)           \> $v - u$                 \> T \\
	(b)           \> $v - A$                 \> F \\
	(c)           \> $A - v$                 \> T \\
	(d)           \> $A + \alpha(B-A)$       \> T \\
	(e)           \> $\alpha A + v$          \> F \\
	\end{tabbing}
	
	\item (5 points)
	Find a homogeneous-coordinate representation of a plane. Hint: the answer will be a dot product.
	
	\item (15 points)
	If we are interested in only two-dimensional graphics, we can use three-dimensional homogeneous coordinates by representing a point as $p = [x~y~1]^T$ and a vector as $v = [a~b~0]^T$. \\
	Find the 3x3 rotation, translation, scaling, and shear matrices R,T,S, and H, respectively. How many degrees of freedom are there in an affine transformation for transforming two-dimensional points?
	
	\item (15 points)
	Derive a rotation matrix where we rotate first about the x-axis $R_x(\theta_x)$, then about the y-axis $R_y(\theta_y)$, and then about the z-axis $R_z(\theta_z)$. Assume that the fixed point is the origin.
	
	$$\left[
	\begin {array}{ccc}
	9 & 13& 17\\
	14& 18& 22
	\end {array}
	\right]$$

\end{enumerate}
\end{document}